Bayesian MCMC diagnostics and summarisation using Tracer 1.6

### 2017-08-03 manuscript/tracer16.tex
add other similar software

>>>>

A key feature of Tracer lies in its ability to link together samples from quantitative random variable log files and tree log files.
This linkage is not available in other popular post-processing MCMC software, such as coda \citep{plummer2006coda} and AWTY \citep{nylander2007awty}, and enables users to approximate the posterior distribution of scientifically relevant quantities that are functions of both the tree and other quantitative measures.
Demographic reconstruction through time is a prime example.
